---
title: "Gravid_Females_Castration"
output:
  html_document: default
  pdf_document: default
date: "2025-02-12"
---
#Libraries
```{r Lets load some libraries!}
#Libraries
library(ggplot2)
library(tidyverse)
library(dplyr)
library(readr)
library(forcats)
library(ggrepel)
library(ggpubr)
library(gghalves)
library(stringr)
library(patchwork)

#For models
library(DHARMa)
library(glmmTMB)

```

Set theme for ggplot
```{r Themes}
#Theme set
theme_set(  theme(legend.position = "none",
                  strip.background = element_rect(fill = "White"),
                  panel.background = element_rect(fill = "white",
                                                  colour = "black"), 
                  panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank(), 
                  strip.text = element_text(size = 15),
                    axis.text.y = element_text(size = 15),
                    axis.text.x = element_text(size = 15),
                    axis.title.x = element_text(size = 18),
                    axis.title.y = element_text(size = 18, angle =90, 
                                                margin = margin(r = 15)),
                    strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm")))) 

##TREATMENT COLOURS

treatment_cols <- c(
  "UNEX"     = "#6B7280",
  "INF"      = "#8C2F39",
  "EXP_KJER" = "#2F6F6B",
  "EXP_MER"  = "#9FD6CC")

treatment_cols_gross <- c(
  "UNEX"     = "#6B7280",
  "INF"      = "#8C2F39",
  "EXP"  = "#9FD6CC")


```

Loading the raw data
```{r Raw Data Files}
gravid <- read_csv("GRAVID_CLUTCH_2026.csv")
nursery <- read_csv("F1_SURVIVAL_2026.csv")
```

```{r Data cleaning}
grav <- gravid %>%
        mutate(Strain = as.factor(STRAIN), 
               Stock = as.factor(Stock),
               Infection_Status = as.factor(Infection_Status), 
               Temporary_ID = as.factor(Temporary_ID),
               ID = as.factor(ID),
               Clutch_Tot = Clutch_Est_R + Clutch_Est_L,
               #here 1 means perfect sym. smaller values indicate
               #greater asymetry
               Clutch_Sym = pmin(Clutch_Est_R,Clutch_Est_L) /
                            pmax(Clutch_Est_R,Clutch_Est_L)) %>%
          #remove all those not qualified
        filter(!Infection_Status %in% c("RMV", "INF_MALE_MATE" ))%>%
        filter (!ID %in% c("E_16S")) %>% #
        #let's clean this up a bit
        select(-Initials, -COMBO_FoodRenew, -Last_Checked, -Notes, 
               -`IMAGEJ14_DAY PICUTRE`, -...20, -...22, -STRAIN)

grav %>%
  distinct(ID, Infection_Status) %>%
  count(Infection_Status) %>%
  mutate(prop = n / sum(n))

nurse <- nursery %>%
    mutate(
    ID = case_when(
      # Case 1: Already correctly formatted
      str_starts(MUM_ID, "GR_") ~ MUM_ID,

      # Case 2: MUM_ID is like "81E", "92G", etc.
      str_detect(MUM_ID, "^[0-9]+[A-Za-z]+$") ~ paste0("GR_", MUM_ID),

      # Case 3: MUM_ID like "Eii", use Temporary_ID + stripped stock letter
      TRUE ~ paste0("GR_", Temporary_ID, str_remove(MUM_ID, "i+")))) %>%
      select(-starts_with("..."), -DAD_ID, -Notes) %>%
      filter( !MUM_ID %in% c("E_16S")) %>% #She's an F1, no need for that.
      
      mutate(DOB = parse_date_time(DOB,orders = c("d%b%Y", "d%b%y")))


```

# Future things (with more data once experiment concluded)
+ Longevity
+ Infection susceptibilitY
+Proportion survival (nauplii/eggs)

```{r Data joining + More Tidying}
grav1 <- grav %>%
  #remove gravid from starvation experiment
        #Timing
         mutate(Date_Gravid = parse_date_time(Date_Gravid, 
                                           orders = c("d%b%Y", "d%b%y")),
                Date_Drop = parse_date_time(Date_Drop, 
                                           orders = c("d%b%Y", "d%b%y")),
                Holding_Time = as.numeric(as.duration(Date_Drop - Date_Gravid), "days"), 
                # Calculate the clutch holding time in days 
                Date_Iso= parse_date_time(Date_Iso,orders = c("d%b%Y", "d%b%y")),
                Death_Date = parse_date_time(Death_Date, 
                                          orders = c("d%b%Y", "d%b%y"))) %>% 
  #Days between clutches
        arrange(ID, Date_Gravid) %>%  # Sort by female and Date_Gravid
        group_by(ID) %>%  # Group by female ID
        mutate( Next_Date_Gravid = lead(Date_Gravid),  
    # Get the next Date_Gravid for each female
      Time_Between_Clutches = 
              as.numeric(as.Date(Next_Date_Gravid, format = "%d%b%y") - 
              as.Date(Date_Drop, format = "%d%b%y")), 
        age_post_iso = as.numeric(Death_Date - Date_Iso)) %>%
        ungroup() 

grav1$Infection_Status <- forcats::fct_relevel(grav1$Infection_Status,
                                              c("UNEX","EXP","INF"))

grav_all <- grav1 %>%
            left_join( nurse %>% select(ID, Clutch_Num, Maximum_Dens, DOB),
              by = c("ID", "Clutch_Num") ) %>%
             group_by(ID, Clutch_Num) %>%
            mutate( prp_survival = Maximum_Dens / Clutch_Tot ) %>%
            ungroup() %>%
            mutate(
              Treatment_Fine = case_when(
                Infection_Status == "INF" ~ "INF",
                Infection_Status == "UNEX" ~ "UNEX",
                Infection_Status == "EXP" & Strain == "KJER" ~ "EXP_KJER",
                Infection_Status == "EXP" & Strain == "MER"  ~ "EXP_MER",
                TRUE ~ NA_character_ ) )

grav_all <- grav_all %>%
           mutate(is_post = Clutch_Num != 1,
    
            # Row-level post-treatment values (NA for clutch 1 so they don't contribute to sums)
            Clutch_Tot_post     = ifelse(is_post, Clutch_Tot, NA_real_),
            Maximum_Dens_post   = ifelse(is_post, Maximum_Dens, NA_real_),
            prp_survival_post   = ifelse(is_post, prp_survival, NA_real_)  ) %>%
 
           group_by(ID) %>%
           mutate(
              # Female-level post-treatment totals repeated on every row for that female
              PostTreat_Eggs_Ind     = sum(Clutch_Tot_post, na.rm = TRUE),
              PostTreat_Nauplii_Ind  = sum(Maximum_Dens_post, na.rm = TRUE),
          
              # Did she produce any post-treatment clutch rows at all?
              has_post_clutch = any(is_post & !is.na(Clutch_Tot)),
          
              # Did she hatch any nauplii post-treatment?
              has_post_hatch  = any(is_post & !is.na(Maximum_Dens) & Maximum_Dens > 0),

          # Oldest post-treatment nonzero hatch age; 0 if none
          Oldest_nonzero_F1_minusfirst = ifelse(
            has_post_hatch,
            as.numeric(max(DOB[is_post & !is.na(Maximum_Dens) & Maximum_Dens > 0], 
                           na.rm = TRUE) - 
                         Date_Iso), 0 ) ) %>%
              ungroup()


####################################
####################################
#### to avoid pseudo-replication ####
grav_byfemale <- grav_all %>%
              group_by(ID, Strain) %>%
               summarise( PostTreat_Eggs_Ind = sum(Clutch_Tot[Clutch_Num != 1], 
                                                          na.rm = TRUE),
                                PostTreat_Nauplii_Ind = sum(Maximum_Dens[Clutch_Num != 1], 
                                                            na.rm = TRUE),
                    
                               Oldest_nonzero_F1_minusfirst =  ifelse(
                                  all(Maximum_Dens[Clutch_Num != 1] <= 0 | 
                                      is.na(Maximum_Dens[Clutch_Num != 1])),0,
                                  as.numeric(  max(DOB[Clutch_Num != 1 & Maximum_Dens > 0],
                                                   na.rm = TRUE) -  Date_Iso ) ),
                               
                        max_clutches = max(Clutch_Num),
                        Treatment_Fine = first(Treatment_Fine),
                        Stock = first(Stock),
                        Infection_Status = first(Infection_Status)) %>%
                        ungroup() 

# 1) Universe of females (keeps those with only clutch 1)
grav_byfemale %>%
        distinct(ID, Treatment_Fine) %>%
        group_by(Treatment_Fine) %>%
        summarise(n = n())

```


Trapezoidal rule:
$$
\text{Area} = \frac{1}{2}(y_1 + y_2)(x_2 - x_1)
$$

```{r Calculating integrated prevalence}
library(dplyr)
library(forcats)

# 1) Universe of females (keeps those with only clutch 1)
female_universe <- grav_all %>%
  distinct(ID, Treatment_Fine)

# 2) Integrated reproduction excluding clutch 1
integrated_off_prev <- grav_all %>%
  filter(Clutch_Num != 1) %>%
  select(ID, Treatment_Fine, Clutch_Num, Clutch_Tot, Maximum_Dens) %>%
  distinct() %>%
  arrange(ID, Clutch_Num) %>%
  group_by(ID, Treatment_Fine) %>%
  mutate(
    dx = Clutch_Num - lag(Clutch_Num),

    avg_egg  = (Clutch_Tot + lag(Clutch_Tot)) / 2,
    area_egg = dx * avg_egg,

    avg_naup  = (Maximum_Dens + lag(Maximum_Dens)) / 2,
    area_naup = dx * avg_naup ) %>%
  summarise(
    integrated_egg     = sum(area_egg, na.rm = TRUE),
    integrated_nauplii = sum(area_naup, na.rm = TRUE),

    # For females with exactly one post-first clutch, max-min = 0
    time_span = max(Clutch_Num) - min(Clutch_Num),

    mean_egg_int = ifelse(time_span > 0, integrated_egg / time_span, 0),
    mean_nauplii_int = ifelse(time_span > 0, integrated_nauplii / time_span, 0),
    n_post_clutches = n(),
    .groups = "drop" )

# 3) Bring back females who had no post-first clutches; set their values to 0
integrated_off_prev <- female_universe %>%
  left_join(integrated_off_prev, by = c("ID", "Treatment_Fine")) %>%
  mutate(
    integrated_egg     = coalesce(integrated_egg, 0),
    integrated_nauplii = coalesce(integrated_nauplii, 0),
    time_span          = coalesce(time_span, 0),
    mean_egg_int       = coalesce(mean_egg_int, 0),
    mean_nauplii_int   = coalesce(mean_nauplii_int, 0),
    n_post_clutches    = coalesce(n_post_clutches, 0)
  )

integrated_off_prev$Treatment_Fine <- fct_relevel(integrated_off_prev$Treatment_Fine, "UNEX")

# 4) Treatment-level summary (unchanged)
integrated_by_treatment <- integrated_off_prev %>%
  group_by(Treatment_Fine) %>%
  summarise(
    mean_int_egg = mean(integrated_egg, na.rm = TRUE),
    se_int_egg   = sd(integrated_egg, na.rm = TRUE) / sqrt(n()),

    mean_int_naup = mean(integrated_nauplii, na.rm = TRUE),
    se_int_naup   = sd(integrated_nauplii, na.rm = TRUE) / sqrt(n()),

    n_females = n(),
    .groups = "drop"
  )

###################
### PLOT PLOT PLOT ###
###################
integrated_off_prev %>%
  ggplot(aes(x = Treatment_Fine, y = integrated_egg,
             #integrated_egg_prevalence
             colour = Treatment_Fine)) +
  geom_jitter( height = 0, width = 0.05, alpha = 0.8, 
               size = 5)+
  stat_summary(geom = "pointrange", 
               fun.data = mean_cl_boot,
               shape = 21, 
               stroke = 2,
               fill = "white",
               colour = "black",
               size = 1)+
  scale_color_manual(values = treatment_cols) +
  scale_x_discrete(labels = c( "UNEX"     = "Unexposed",
  "EXP_MER"  = "Exposed (Foreign)", "EXP_KJER" = "Exposed (Local)",
  "INF"      = "Infected")) +
  labs(x = "", 
       y = "Integrated mean egg production
(minus first clutch)") +
theme(strip.text = element_text(size = 18),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 20, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm"))) 



integrated_off_prev %>%
  ggplot(aes(x = Treatment_Fine, y = integrated_nauplii,
             #integrated_egg_prevalence
             colour = Treatment_Fine)) +
  geom_jitter( height = 0, width = 0.05, alpha = 0.8, 
               size = 5)+
  stat_summary(geom = "pointrange", 
               fun.data = mean_cl_boot,
               shape = 21, 
               stroke = 2,
               fill = "white",
               colour = "black",
               size = 1)+
  scale_color_manual(values = treatment_cols) +
  scale_x_discrete(labels = c( "UNEX"     = "Unexposed",
  "EXP_MER"  = "Exposed (Foreign)", "EXP_KJER" = "Exposed (Local)",
  "INF"      = "Infected")) +
  labs(x = "", 
       y = "Integrated mean egg production
(minus first clutch)") +
theme(strip.text = element_text(size = 18),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 20, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm"))) 

```

#############################
## TAKING A LOOK INTO EGGS! ##
#############################
Are we even across clutches?
We do not find singificant differences in the clutch size at time of isolation between experimental treatments (-- except unex is smaller).
```{r Isolation: Experimental treamtments Clutch Numbers}

grav_all %>%
    filter(Clutch_Num == 1) %>%
   # group_by(Infection_Status) %>%
    summarise(mean_1 = mean(Clutch_Tot)) 

test<- grav_all %>%
    filter(Clutch_Num == 1) %>%
   # filter(!Treatment_Fine == "UNEX") %>%
    select(Clutch_Tot, Treatment_Fine, Stock) %>%
    ungroup()

test1<- aov(Clutch_Tot ~ Treatment_Fine, data= test)
test1<- kruskal.test(Clutch_Tot~ Treatment_Fine, data= test)

summary(test1)

test$Treatment_Fine<- fct_relevel(test$Treatment_Fine, "EXP_KJER")
eg1<- glmmTMB(Clutch_Tot~ Treatment_Fine + (1|Stock),
              family = nbinom1,
              data = test)
summary(eg1)
simusimulationOutput <- simulateResiduals(fittedModel = eg1, plot = T)
testDispersion(eg1)
testZeroInflation(eg1)

test.0<- grav_all %>%
    filter(Clutch_Num == 1) %>%
    group_by(Treatment_Fine) %>% #Infection_Status
    mutate(mean_1 = mean(Clutch_Tot)) %>%
    select(mean_1, Treatment_Fine)


kruskal.test(mean_1 ~ Infection_Status, data= test)
test2<- aov(mean_1 ~ Treatment_Fine, data= test.0)
kruskal.test(mean_1 ~ Treatment_Fine, data= test.0)
summary(test2)
TukeyHSD(test2)

t.test(mean_1 ~ Infection_Status, data= test)



grav_all %>%
    #filter(Clutch_Num == 1) %>%
    group_by(Infection_Status) %>%
    summarise(mean_age = mean(age_post_iso, na.rm = T)) 

grav_byfemale %>%
    #filter(Clutch_Num == 1) %>%
    group_by(Infection_Status) %>%
    summarise(mean_max = mean(max_clutches)) 

```

Is it castration?
```{r Castration Numbers}

#COMBINE EFFORTS OF ALL FEMALES within each treatment
grav_byfemale %>%
  group_by(Treatment_Fine) %>%
  summarise(total_nauplii = sum(PostTreat_Nauplii_Ind, na.rm = TRUE)) %>%
  ggplot(aes(x = Treatment_Fine, y = total_nauplii)) +
  geom_col(fill = "grey70", width = 0.6) +
  geom_text(aes(label = total_nauplii)) +
  labs(y = "Total nauplii hatched (count, post-treatment, all females)", 
       x = "")

```

Very exciting developments, so here are the clutch numbers which are the numbers of eggs in each clutch (which we counted individually for each side!). Be mindful I often subtract the first clutch away from visualizations/models -- this is because this is the clutch when the female was **isolated** before we applied any treatments. So it does not reflect our experiment. 

```{r Clutch Numbers + Symm. Visualization }

grav1 %>%
  ggplot(aes(x = Clutch_Num, y = Clutch_Tot)) +
  geom_point()+
  facet_wrap(~Stock)

#####
#Clutch numbers across time
#####

grav_all %>%
  group_by(Infection_Status, Clutch_Num) %>%
  mutate( mean_eggs_exp_clutch = mean(Clutch_Tot)) %>%
  ggplot(aes(x = Clutch_Num, y = Clutch_Tot, 
             colour = Infection_Status)) +
    annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.5, 
           ymin = -Inf, ymax = Inf)+
  geom_jitter(height = 0, width = 0.00, size = 3,
              alpha = 0.3)+
  
  facet_wrap(~  Infection_Status )+ #Strain +
geom_point(aes(x = Clutch_Num, y = mean_eggs_exp_clutch),
             size = 3)+
  stat_summary(geom = "pointrange", 
               fun.data = mean_cl_boot,
               colour = "black")+
 geom_line(aes(x = Clutch_Num, 
                y = mean_eggs_exp_clutch, 
                group = 1), 
            colour = "black", 
            linetype = "dashed") +
  xlab("Clutch number (n+1)")+
  ylab("Total eggs per clutch (count)") +
  scale_x_continuous(breaks = seq(0, 14, by = 2))+
  scale_color_manual(values = treatment_cols_gross)



#Let's get this all leveled up in a cute way
grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, c("UNEX", "INF"))
  
grav_all %>%
  group_by(Treatment_Fine, Clutch_Num) %>%
  mutate( mean_eggs_exp_clutch = mean(Clutch_Tot)) %>%
  ggplot(aes(x = Clutch_Num, y = Clutch_Tot, 
             colour = Treatment_Fine)) +
    annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.5, 
           ymin = -Inf, ymax = Inf)+
  geom_jitter(height = 0, width = 0.00, size = 3,
              alpha = 0.3)+
  
  facet_wrap(~  Treatment_Fine )+ #Strain +
geom_point(aes(x = Clutch_Num, y = mean_eggs_exp_clutch),
             size = 3)+
  stat_summary(geom = "pointrange", 
               fun.data = mean_cl_boot,
               colour = "black")+
 geom_line(aes(x = Clutch_Num, 
                y = mean_eggs_exp_clutch, 
                group = 1), 
            colour = "black", 
            linetype = "dashed") +
  xlab("Clutch number (n+1)")+
  ylab("Total eggs per clutch (count)") +
  scale_x_continuous(breaks = seq(0, 14, by = 2))+
  scale_color_manual(values = treatment_cols)

A<- 
  grav_all %>%
  filter(!Treatment_Fine %in% c("UNEX", "INF")) %>%
  #group_by(Clutch_Num, Treatment_Fine) %>%
  #filter(n() > 1) %>%        # <- drop singleton clutches
  #ungroup() %>%
  ggplot(aes(x = as.factor(Clutch_Num), y = Clutch_Tot, 
             colour = Treatment_Fine)) +
  annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.25, 
           ymin = -Inf, ymax = Inf)+
 # geom_point(size = 2.5, alpha = 0.4)+
stat_smooth(method = "gam", 
              aes(group = Treatment_Fine),
              fullrange = F, 
              se = F,
              fill = "lightgrey",
              formula = y ~ s(x, bs = "cr", k = 5))+
    stat_summary(fun.data = mean_cl_boot,
                 shape = 21, size = 0.7, 
                 fill = "white",
               aes(group =Treatment_Fine),
               geom= "pointrange")+
    theme(axis.text.y = element_text(size = 22),
          axis.text.x = element_text(size = 22)) +
  labs( x = "", 
        y = "") +
  scale_color_manual(values =  c( "#2F6F6B","#9FD6CC")) 

A

ggsave("EXP_eggs.png", A, width = 6, height = 8, units = "in" )

#####
#Clutch symmetry
#####

# Plot
grav_all %>%
  ggplot(aes(x = factor(Clutch_Num), y = Clutch_Sym, 
             fill = Infection_Status)) +

  geom_boxplot(width = 0.3, outlier.shape = NA, alpha = 0.7) + 
  #geom_jitter(width = 0.1, size = 2, alpha = 0.5) +  # Raw data points
  geom_hline(yintercept = 1, linetype = "dashed", color = "black") +
  facet_wrap(~Infection_Status) +
  xlab("Clutch Number (n+1)") +
  ylab("Clutch Symmetry") +
  scale_fill_manual(values = treatment_cols_gross)

grav_all %>%
  ggplot(aes(x = Clutch_Est_L, 
             y = Clutch_Est_R, 
             color = Infection_Status)) +
  geom_abline(slope = 1, 
              intercept = 0, linetype = "dashed", 
              color = "black") +
  geom_point(alpha = 0.7, size = 3) +
  facet_wrap(~Infection_Status ) + #+ Clutch_Num
  xlab("Left Clutch Size") +
  ylab("Right Clutch Size") +
  scale_color_manual(values = treatment_cols_gross) 
  
  
#####
#Lifetime Clutch Production
#####
grav_all <- grav_all%>%
  mutate( Strain = fct_explicit_na(Strain, na_level = "None"),
          Strain = fct_recode(Strain, "Local" = "MER", "Foreign" = "KJER"),
          Strain = fct_relevel(Strain, c("None", "MER")))


grav_all %>%
  ggplot(aes(x = Infection_Status, y = PostTreat_Eggs_Ind, 
             colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 4, alpha = 0.3) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  facet_wrap(~Strain, scales = "free_x")+
  scale_color_manual(values = treatment_cols) +
  labs(x = "", 
       y = "Individual lifetime egg production
  (count; -1st clutch)") +
  theme(strip.text = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 18, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm"))) 
  
  
```

```{r Clutch Numbers Models}

#################
## Total eggs per clutch #
#################

#1. Clutch size decreases across time

#grav_all is not stable, neither is grav
grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, "UNEX") #"EXP_MER"


#okay, so i don't want to include the first clutch, but then all the females that do not even make another clutch are not counted?
m1 <- 
  grav_all %>%
  filter(!Clutch_Num == 1) %>% 
  #do not include first clutch; pre-treatment
  glmmTMB(Clutch_Tot ~ Clutch_Num * Treatment_Fine + 
                            #Clutch_Sym + 
                            Time_Between_Clutches+
                            (1| Stock) + (1|ID),
   #[add age at clutch number] 
              dispformula = ~ 1,
              ziformula = ~ 1,
              family = nbinom1, #nbinom1, poisson, nbinom2
              data = .)

simusimulationOutput <- simulateResiduals(fittedModel = m1, plot = T)
summary(m1)

m1.0 <- 
  grav_all %>%
  filter(!Clutch_Num == 1) %>% 
  #do not include first clutch; pre-treatment
  glmmTMB(Clutch_Tot ~ Clutch_Num * Treatment_Fine + 
                            #Clutch_Sym + 
                            Time_Between_Clutches+
                            (1| Stock) + (1|ID),
   #[add age at clutch number] 
              dispformula = ~  Clutch_Num,
              #ziformula = ~ Clutch_Num ,
              family = nbinom1, #nbinom1, poisson, nbinom2
              data = .)


simusimulationOutput <- simulateResiduals(fittedModel = m1, plot = T)
summary(m1)
testDispersion(m1)


#################
## Lifetime egg production #
#################

## HERE WE NEED 1 LINE PER FEMALE. THIS IS PSEUDO REPLICATION.

grav_byfemale$Treatment_Fine <- fct_relevel(grav_byfemale$Treatment_Fine, 
               "UNEX") #"EXP_MER", EXP_KJER"

#both of these are fine

m2 <- glmmTMB(PostTreat_Eggs_Ind ~ Treatment_Fine + (1| Stock), 
             # dispformula = ~ 1 ,
              family = nbinom1, 
              data = grav_byfemale)

summary(m2)
simusimulationOutput <- simulateResiduals(fittedModel = m2, plot = T)
testDispersion(m2)
testZeroInflation(m2)


#################
## Number of clutches #
#################

m3<- glmmTMB(max_clutches ~ Treatment_Fine + (1| Stock), 
             dispformula = ~ 1 ,
             #ziformula = ~ Treatment_Fine,
              family = poisson, #nbinom1, nbinom2, poisson
              data = grav_byfemale)

summary(m3)
simusimulationOutput <- simulateResiduals(fittedModel = m3, plot = T)
testDispersion(m3)
grav_byfemale %>%
        group_by(Treatment_Fine) %>%
        summarize(mean_clutches = mean(max_clutches-1), #remove isolation clutch
                  se_clutches = sd(max_clutches-1, na.rm = T)/sqrt(n())) %>%
        ungroup()

```

#Clutch Timing
Questions: 

1. How long are females holding onto their clutches? Here we can think about the cost of carrying these enomours things around, potential predation. We can also think about total output-- fast these guys hatch, faster she can churn out another clutch.

2. Time between clutches. Here I would hypothesize that it would take more and more time to generate clutches, as females are getting older, and this is quite a costly endeavor.

#How long/How many clutches does stored sperm fertilize?

```{r Timing of Clutches (inter-intra) + Survival }

#Holding time and inter-clutch intervals are averaged within females prior to treatment-level summaries to avoid pseudoreplication arising from repeated clutches per individual.

per_female_timing <- grav_all %>%
                      group_by(Treatment_Fine, ID, Stock) %>%
                      summarise(
                        max_clutches = max(Clutch_Num, na.rm = T),
                        mean_holding_time = mean(Holding_Time, na.rm = TRUE),
                        mean_time_between = mean(Time_Between_Clutches, na.rm = TRUE),
                        max_age_f1 = max(Oldest_nonzero_F1_minusfirst, na.rm = T), 
                        #age when they had last viable egg
                        max_age = max(age_post_iso, na.rm = T),  #age of mum
                        .groups = "drop" ) %>%
                        filter(is.finite(max_age_f1), 
                               is.finite(max_age))

#Now bring it all together

per_treatment_timing <- per_female_timing %>%
                    group_by(Treatment_Fine) %>%
                    summarise(
                      n_females = n(),
                      #time holding a single clutch
                      Average_Holding_Time = mean(mean_holding_time, na.rm = TRUE),
                      Median_Holding_Time  = median(mean_holding_time, na.rm = TRUE),
                      se_Holding_Time      = sd(mean_holding_time, na.rm = TRUE) / sqrt(n_females),
                      
                      #time between clutches
                      Average_Time_Between_Clutches = mean(mean_time_between, na.rm = TRUE),
                      Median_Time_Between_Clutches  = median(mean_time_between, na.rm = TRUE),
                      se_timebtwn = sd(mean_time_between, na.rm = TRUE) / sqrt(n_females),
                  
                      #Age related
                       mean_max_age_f1 = mean(max_age_f1, na.rm = T), 
                       se_f1 = sd(max_age_f1, na.rm = TRUE) / sqrt(n_females),
                  
                       mean_max_age = mean(max_age , na.rm = T),
                       se_age = sd(max_age , na.rm = TRUE) / sqrt(n_females),
                      .groups = "drop" )

############# #############
## Plots ## Plots ## Plots
############# #############

A<- 
  ggplot(per_treatment_timing, aes(x = Treatment_Fine, y = Average_Holding_Time)) +
  geom_hline(yintercept = c(1, 3, 5), linetype = "dashed", 
                    colour = "grey", size = 0.4) +
  geom_errorbar(aes( ymin = Average_Holding_Time - se_Holding_Time,
                ymax = Average_Holding_Time + se_Holding_Time), width = 0.2) +
  geom_point(size = 6, aes(fill = Treatment_Fine), shape = 21) +
  labs(y = "Intra-clutch time 
(days female holds a clutch)", x = "") +
  scale_fill_manual(values = treatment_cols)

B<- 
  ggplot(per_treatment_timing, aes(x = Treatment_Fine, y = Average_Time_Between_Clutches)) +
            geom_hline(yintercept = c(1, 3, 5, 7), linetype = "dashed", 
                    colour = "grey", size = 0.4) +
  geom_errorbar(aes( ymin = Average_Time_Between_Clutches -  se_timebtwn,
                ymax = Average_Time_Between_Clutches +  se_timebtwn), width = 0.2) +
  geom_point(size = 6, aes(fill = Treatment_Fine), shape = 21) +
  labs(y = "Inter-clutch time
(days between clutches)", x = "") +
  scale_fill_manual(values = treatment_cols)


C<- 
  ggplot(per_treatment_timing, aes(x = Treatment_Fine, y = mean_max_age_f1)) +
        geom_errorbar(aes( ymin = mean_max_age_f1 -  se_f1,
                        ymax = mean_max_age_f1 +  se_f1), width = 0.2) +
        geom_hline(yintercept = c(7, 14, 21, 30), linetype = "dashed", 
                    colour = "grey", size = 0.4) +
          geom_point(size = 6, aes(fill = Treatment_Fine), shape = 21) +
          labs(y = "Oldest age at which 
female had viable F1 (days)", x = "") +
          scale_fill_manual(values = treatment_cols)

D<- 
  ggplot(per_treatment_timing, aes(x = Treatment_Fine, y = mean_max_age)) +
        geom_errorbar(aes( ymin = mean_max_age -  se_age,
                        ymax = mean_max_age +  se_age), width = 0.2) +
          geom_point(size = 6, aes(fill = Treatment_Fine), shape = 21) +
         geom_hline(yintercept = c(30, 60, 90), linetype = "dashed", 
                    colour = "grey", size = 0.4) +
          labs(y = "Survival post-isolation (days)", x = "") +
          scale_fill_manual(values = treatment_cols)


E<- (A+B)/(C+D)
E
ggsave("timing_birth_death.png", E, width = 10, height = 8, units = "in")

```

# Survival Curves
```{r Survival Curves}

library(survminer)

require("survival")
fit <- survfit(Surv(age_post_iso) ~ Treatment_Fine, data = grav_all)

ggsurvplot(fit, data = grav_all, 
           size = 1,                 # change line size
  palette = c(  "#6B7280", "#9FD6CC", "#8C2F39","#2F6F6B"),# custom color palettes
  conf.int = F,         # Add confidence interval # Risk table color by groups
  xlab = "Survival post-isolation (days)",
 legend.labs =   c("Unexposed", "Exposed (Local)", "Infected", "Exposed (Foreign)"), 
 ggtheme = theme( axis.text.y = element_text(size = 15),
                    axis.text.x = element_text(size = 15),
                    axis.title.x = element_text(size = 18),
                    axis.title.y = element_text(size = 18, angle =90, 
                                                margin = margin(r = 15)))) 



```


```{r Clutch Timing Models}
per_female_timing$Treatment_Fine <- fct_relevel(per_female_timing$Treatment_Fine, "UNEX")

#Intra Clutch time
#How many days to females hold clutches?
#Summarized by female, could also do per/cluctch

mean(per_female_timing$mean_holding_time)

t1 <- 
  per_female_timing %>%
  glmmTMB(log(mean_holding_time+1) ~ Treatment_Fine  + (1|Stock), 
                          family = gaussian, #gaussian, Gamma(link = "log")
                         dispformula  = ~ Treatment_Fine, 
                         # weights = max_clutches,
                          #ziformula = ~Treatment_Fine,
                          data = .)
summary(t1)
simusimulationOutput <- simulateResiduals(fittedModel = t1, plot = T)
testDispersion(t1)
testZeroInflation(t1)


### Inter Clutch time
#TIME BETWEEN CLUTCHES

per_female_timing$Treatment_Fine <- fct_relevel(per_female_timing$Treatment_Fine,
                                              "UNEX") #"UNEX", "EXP_MER

t2 <- glmmTMB(log(mean_time_between+1) ~ Treatment_Fine  + (1|Stock), 
                          family = gaussian,
                          dispformula  = ~ Treatment_Fine, 
                          #ziformula = ~Treatment_Fine,
                          data = per_female_timing)

summary(t2)
simusimulationOutput <- simulateResiduals(fittedModel = t2, plot = T)
testDispersion(t2)
testZeroInflation(t2)

##############################
# Fecundity Window (Oldest F1)

per_female_timing$Treatment_Fine <- fct_relevel(per_female_timing$Treatment_Fine,
                                              "UNEX") #"UNEX", "EXP_MER

t3 <- glmmTMB(max_age_f1 ~ Treatment_Fine   + (1|Stock), #log(max_age_f1+1)
                          family = nbinom1, #gaussian
              #Gamma(link = "log")
                          #dispformula  = ~ Treatment_Fine, 
                          #weights = max_clutches,
                          ziformula = ~1,
                          data = per_female_timing)

summary(t3)
simusimulationOutput <- simulateResiduals(fittedModel = t3, plot = T)
testDispersion(t3)
testZeroInflation(t3)


# Survival post isolation
per_female_timing$Treatment_Fine <- fct_relevel(per_female_timing$Treatment_Fine,
                                              "UNEX") #"UNEX", "EXP_MER

t4 <- glmmTMB(log(max_age+1)  ~ Treatment_Fine  + (1|Stock), 
                          family = gaussian,
                          data = per_female_timing)


summary(t4)
simusimulationOutput <- simulateResiduals(fittedModel = t4, plot = T)
testDispersion(t4)
testZeroInflation(t4)


```

#F1 Survival
(do that one nature paper survival filtering thing)

**Note how the survival dynamics change across clutch number.** 
Why are females still producing clutches (something that takes up a lot of energy and is surely costly in many other aspects as well (i.e. predation)) when the survival of her offspring ends up being so low?

What's really interesting here is that we are seeing infected females continue to produce eggs (albeit at a much lower rate and for a much lesser time) with a close to 0 survival rate. This makes me think about mechanism. They are physically **able** to produce some eggs (sometimes, don't forget about ghost clutches), but really none of them survive. Maybe the worm is disrupting the allocation of yummy juicy stuff to eggs?

```{r Nauplii: How are the babies surviving from eggs}

#Proportion of hatching nauplii from eggs

grav_all1 <- grav_all %>%
  mutate( #Strain = fct_explicit_na(Strain, na_level = "None"),
          Treatment_Fine = fct_recode( Treatment_Fine,
                              "Unexposed" = "UNEX", "Infected" = "INF",
                              "Exposed: Local" = "EXP_MER", "Exposed: Foreign" = "EXP_KJER"),
           Treatment_Fine = fct_relevel( Treatment_Fine, c("Unexposed", "Infected")))

grav_all1 %>%
  filter(!prp_survival > 1) %>% #a couple of weird rows
  ggplot(aes(x = as.factor(Clutch_Num), y = prp_survival, 
             colour = Treatment_Fine)) +
  annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.25, 
           ymin = -Inf, ymax = Inf)+
  geom_point(size = 2.5, alpha = 0.7)+
  stat_summary(fun.data = mean_cl_boot,
               colour = "black",
               aes(group =Treatment_Fine),
               geom= "pointrange")+
    stat_summary(fun.data = mean_cl_boot,
               colour = "black",
               aes(group = Treatment_Fine),
               linetype = "dashed",
               geom= "line")+
  facet_wrap(~Treatment_Fine)+ #, scales = "free_x"
  labs( x = "Clutch number (n + 1)", 
        y = "Proportion of nauplii hatching from clutch") +
  scale_color_manual(values =  c( "#6B7280", "#8C2F39","#2F6F6B","#9FD6CC"))


A<- 
  grav_all1 %>%
  filter(!Treatment_Fine %in% c("Unexposed", "Infected")) %>%
  group_by(Clutch_Num, Treatment_Fine) %>%
  filter(n() > 1) %>%        # <- drop singleton clutches
  ungroup() %>%
  ggplot(aes(x = as.factor(Clutch_Num), y = prp_survival, 
             colour = Treatment_Fine)) +
  annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.25, 
           ymin = -Inf, ymax = Inf)+
 # geom_point(size = 2.5, alpha = 0.4)+
stat_smooth(method = "gam", 
              aes(group = Treatment_Fine),
              fullrange = F, 
              se = F,
              fill = "lightgrey",
              formula = y ~ s(x, bs = "tp", k = 6))+
    stat_summary(fun.data = mean_cl_boot,
                 shape = 21, size = 0.7, 
                 fill = "white",
               aes(group =Treatment_Fine),
               geom= "pointrange")+
  ylim(0, 0.7)+
  labs( x = "Clutch number (n + 1)", 
        y = "Proportion of nauplii hatching from clutch") +
  scale_color_manual(values =  c( "#2F6F6B","#9FD6CC")) 

A
ggsave("prp_acrossclutches.png", A, height = 6.5, width = 5, units = 
         "in")

#####
#Lifetime nauplii Production
#####

grav_all %>%
  ggplot(aes(x = Infection_Status, y = PostTreat_Nauplii_Ind, 
             colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 4, alpha = 0.3) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  facet_wrap(~Strain, scales = "free_x")+
  scale_color_manual(values = treatment_cols) +
  labs(x = "", 
       y = "Individual lifetime nauplii production
  (count; -1st clutch, post-isolation)") +
  theme(strip.text = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 18, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm")))



grav_all %>%
  ggplot(aes(x = Infection_Status, y = prp_survival_post, 
             colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 4, alpha = 0.3) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  facet_wrap(~Strain, scales = "free_x")+
  scale_color_manual(values = treatment_cols) +
  labs(x = "", 
       y = "Proportion of nauplii surviving") +
  theme(strip.text = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 18, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm")))


#### 

grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, c("UNEX", "INF"))

#Number of nauplii survivng post-exposure
grav_all%>%
    ggplot(aes(x = Clutch_Tot, y = Maximum_Dens_post, 
             colour = ifelse(Maximum_Dens_post > 0, Treatment_Fine, "Zero"))) +
  geom_point(size = 5, alpha = 0.7)+
  stat_smooth(method = "glm", 
             # formula = y ~ s(x, bs = "tp", k = 2), 
              colour = "black",
              fullrange = F)+
  facet_wrap(~Treatment_Fine)+ #, scales = "free_x"
  coord_cartesian(y = c(0, max(grav_all$Maximum_Dens)),
                  x = c(0, 70))+
  labs(y = "Surviving nauplii 24-hrs post-hatch (count)", 
       x =  "Total eggs per clutch (count)") +
  scale_color_manual(values =  c( "#6B7280",  "#8C2F39", 
                                  "#2F6F6B","#9FD6CC", "lightgrey"))


#Also Not very fun (can delete later)
grav_all %>%
  ggplot(aes(x = Treatment_Fine, y = prp_survival_post, 
             colour = Treatment_Fine)) +
  geom_point(size = 2.5, alpha = 0.7)+
  stat_summary(fun.data = mean_cl_boot,
               colour = "black",
               aes(group =Treatment_Fine),
               geom= "pointrange")+
  labs( x = "", 
        y = "Proportion of nauplii hatching from clutch (-1st clutch)") +
  scale_color_manual(values =  c( "#6B7280", "#8C2F39","#2F6F6B","#9FD6CC"))


```

```{r Nauplii Numbers Models}

#################
## Lifetime Nauplii production #
#################

## HERE WE NEED 1 LINE PER FEMALE. THIS IS PSEUDO REPLICATION.
grav_byfemale$Treatment_Fine <- fct_relevel(grav_byfemale$Treatment_Fine, 
                                                  "EXP_KJER") #"EXP_MER", EXP_KJER"

m3 <- 
  grav_byfemale %>%
  glmmTMB(PostTreat_Nauplii_Ind ~ Treatment_Fine  +
                                   (1| Stock), 
              #dispformula = ~ 1 ,
               ziformula = ~1,
              data = .,
              family = nbinom1)

summary(m3)
simusimulationOutput <- simulateResiduals(fittedModel = m3, plot = T)
testDispersion(m3)
testZeroInflation(m3)


#################
## Proportion of nauplii hatching from clutches #
## Surviving nauplii based on clutch tot
#################

grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, "EXP_KJER")

m4 <- grav_all %>%
  filter(is_post) %>%   # keeps all females; uses only post-treatment clutch rows
  mutate( failures = Clutch_Tot_post - Maximum_Dens_post ) %>%
  filter(!is.na(Maximum_Dens_post), !is.na(Clutch_Tot_post), failures >= 0) %>%
  glmmTMB(
    cbind(Maximum_Dens_post, failures) ~ Treatment_Fine + Clutch_Num +
                                          (1|Stock) + (1|ID),
                                        ziformula = ~1,
                                        family = betabinomial(link = "logit"),
                                        data = . )


simusimulationOutput <- simulateResiduals(fittedModel = m4, plot = T)
summary(m4)
testDispersion(m4)
testZeroInflation(m4)


#Meh
m_hurdle <- glmmTMB(
              Maximum_Dens_post ~ Treatment_Fine + Clutch_Num +
                                   (1|Stock) + (1|ID),
              ziformula = ~ Clutch_Num,
              #dispformula = ~Clutch_Num,
              family = nbinom1(link = "log"),
              data = grav_all)

summary(m_hurdle)
simusimulationOutput <- simulateResiduals(fittedModel = m_hurdle, plot = T)


```

### (Re) Plot from chunks above, but now they are in the same place which is cool 
```{r MEGA PLOT: LIFETIME PRODUCTION OF LIFESTAGES}
##########################
# EGSS PER CLUTCH
####################

#Let's get this all leveled up in a cute way
grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, c("UNEX", "INF"))
  
A <- 
  grav_all %>%
  group_by(Treatment_Fine, Clutch_Num) %>%
  mutate( mean_eggs_exp_clutch = mean(Clutch_Tot)) %>%
  ggplot(aes(x = Clutch_Num, y = Clutch_Tot, 
             colour = Treatment_Fine)) +
    annotate(geom = "rect", alpha = 0.3,
            fill = "lightblue",
           xmin = -Inf, xmax = 1.5, 
           ymin = -Inf, ymax = Inf)+
  geom_jitter(height = 0, width = 0.00, size = 3,
              alpha = 0.3)+
  
facet_wrap(~  Treatment_Fine )+ #Strain +
geom_point(aes(x = Clutch_Num, y = mean_eggs_exp_clutch),
             size = 3)+
  stat_summary(geom = "pointrange", 
               fun.data = mean_cl_boot,
               colour = "black")+
 geom_line(aes(x = Clutch_Num, 
                y = mean_eggs_exp_clutch, 
                group = 1), 
            colour = "black", 
            linetype = "dashed") +
  xlab("Clutch number (n+1)")+
  ylab("Total eggs per clutch (count)") +
  scale_x_continuous(breaks = seq(0, 14, by = 2))+
  scale_color_manual(values = treatment_cols) +
  theme(axis.title.x =  element_text(margin = margin(t = 6)))

ggsave("eggs_per_clutch.png", A, width = 8, height = 7, units = "in")

#######################################################

grav_all <- grav_all %>%
  mutate( Strain = fct_explicit_na(Strain, na_level = "None"),
          Strain = fct_recode(Strain, "Local" = "MER", "Foreign" = "KJER"),
          Strain = fct_relevel(Strain, c("None", "MER")))

A<- 
  grav_all %>%
  ggplot(aes(x = Infection_Status, y = PostTreat_Eggs_Ind, 
             colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 4, alpha = 0.3) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  facet_wrap(~Strain, scales = "free_x")+
  scale_color_manual(values = treatment_cols) +
  labs(x = "", 
       y = "Individual lifetime egg production
  (count, post-isolation)") +
  theme(strip.text = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 17, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm"))) 



B<-
  grav_all %>%
  ggplot(aes(x = Infection_Status, y = PostTreat_Nauplii_Ind, 
             colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0.1, 
              size = 4, alpha = 0.3) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  facet_wrap(~Strain, scales = "free_x")+
  scale_color_manual(values = treatment_cols) +
  labs(x = "", 
       y = "Individual lifetime nauplii production
  (count, post-isolation)") +
  theme(strip.text = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.text.x = element_text(size = 15),
        axis.title.y = element_text(size = 17, angle =90, margin = margin(r = 15)),
        strip.text.x = element_text(margin = margin(0.25,0,0.25,0, "cm")))

C<- A/B
C

ggsave("lifetime_production.png", C, width = 10, height = 14, units = "in")


D<- 
  grav_all %>%
  ggplot(aes(x = Clutch_Num, y = prp_survival_post, colour = Treatment_Fine)) +
  geom_jitter(height = 0, width = 0, size = 4, 
              alpha = 0.1) +
  stat_smooth(
    method = "gam", fill = "lightgrey", fullrange = T, size = 1.5, 
    formula = y ~ s(x, k = 6, bs = "tp"), se = TRUE) +
  #facet_wrap(~Strain, scales = "free_x") +
  scale_color_manual(values = treatment_cols) +
  ylim(0, 1)+
  scale_x_continuous(breaks = seq(0, 16, by =2)) +
  labs(x = "Clutch number (n +1)", y = "Proportion of nauplii hatching from clutch") +
  theme( 
    strip.text = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.text.x = element_text(size = 15),
    axis.title.x = element_text(size = 17),
    axis.title.y = element_text(size = 17, angle = 90, margin = margin(r = 15)),
    strip.text.x = element_text(margin = margin(0.25, 0, 0.25, 0, "cm")) ) 

ggsave("prp_survival.png", D, width = 5, height = 5, units = "in")


########################
### NAUPLII SURVIVAL POST-HATCH #
####################

grav_all$Treatment_Fine <- fct_relevel(grav_all$Treatment_Fine, c("UNEX", "INF"))

#Number of nauplii survivng post-exposure
A<- grav_all%>%
    ggplot(aes(x = Clutch_Tot, y = Maximum_Dens_post, 
             colour = ifelse(Maximum_Dens_post > 0, Treatment_Fine, "Zero"))) +
  geom_point(size = 5, alpha = 0.7)+
  stat_smooth(method = "glm", 
             # formula = y ~ s(x, bs = "tp", k = 2), 
              colour = "black",
              fullrange = F)+
  facet_wrap(~Treatment_Fine)+ #, scales = "free_x"
  coord_cartesian(y = c(0, max(grav_all$Maximum_Dens)),
                  x = c(0, 70))+
  labs(y = "Surviving nauplii 24-hrs post-hatch (count)", 
       x =  "Total eggs per clutch (count)") +
  theme(axis.title.x =  element_text(margin = margin(t = 6)))+
  scale_color_manual(values =  c( "#6B7280",  "#8C2F39", 
                                  "#2F6F6B","#9FD6CC", "lightgrey"))

ggsave("castration.png", A, width = 8, height = 8, units = "in")



```


#Infection strain
Local strain significantly higher intensity + higher infection burden
```{r KJER vs MER infection prevalence/intensity + Treatment counts}

############################
## TREATMENT COUNTS ###
############################

grav %>%
  filter(Infection_Status == "INF") %>%
  group_by(ID, Strain) %>%
  group_by(Strain) %>%
  summarise( n = n_distinct(ID))

grav %>%
  filter(Infection_Status == "EXP") %>%
  group_by(ID, Strain) %>%
  group_by(Strain) %>%
  summarise( n = n_distinct(ID))

grav %>%
  filter(Infection_Status == "UNEX") %>%
  group_by(ID, Strain) %>%
  group_by(Strain) %>%
  summarise( n = n_distinct(ID))

############################
## INFECTION INTENSITY ###
############################

#Dose = 3; didnt count the infection intensity in everything, so the number isn't an exact match
grav_inf_intensity<-
grav %>%
  filter(Infection_Status == "INF") %>%
  group_by(ID, Strain) %>%
  summarise( Inf_Intensity = max(Inf_Intensity, na.rm = TRUE), .groups = "drop" ) 
#Have to drop n = 19 animals because we didn't count infection intensity at the start

ggplot(grav_inf_intensity, aes(x = Strain, y = as.numeric(Inf_Intensity))) +
  geom_jitter(height = 0.05, width = 0.05 ) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               aes(group = Strain),
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  ylim(0, 2.5)+
  labs(y = "Infection intensity ([#worms/infected host]))")

grav_inf_intensity %>%
                    mutate(Inf_Intensity = as.numeric(Inf_Intensity)) %>%
                    group_by(Strain) %>%
                    summarise(mean = mean(Inf_Intensity, na.rm = T), .groups = "drop")

grav_inf_intensity<-
grav_all %>%
  filter(!Infection_Status == "UNEX") %>%
  group_by(ID, Strain) %>%
  summarise( Inf_Intensity = max(Inf_Intensity, na.rm = TRUE), .groups = "drop" ) 
#Have to drop n = 19 animals because we didn't count infection intensity at the start

#all
A<- ggplot(grav_inf_intensity, aes(x = Strain, y = as.numeric(Inf_Intensity), 
                               colour = Strain)) +
  geom_jitter(height = 0.05, width = 0.05, size = 3, 
              alpha = 0.7) +
  stat_summary(fun.data = mean_cl_boot, colour = "black", 
               aes(group = Strain),
               shape = 21, size = 1, stroke =1.5,
               fill = "white") +
  scale_colour_manual(values = c("#2F6F6B", "#9FD6CC"))+
  ylim(0, 2)+
  labs(y = "Infection intensity (#worms/host))", x = "")
  
############################
## INFECTION PREVALENCE ###
############################

grav_prev_summary <- grav%>%
  distinct(ID, Strain, Infection_Status) %>%
  group_by(Strain) %>%
  summarise(
    n      = n(),                                # total females in that strain
    n_inf  = sum(Infection_Status == "INF"),     # infected
    n_exp  = sum(Infection_Status == "EXP"),     # exposed only
    n_trials = n_inf + n_exp,
    inf_prev = n_inf / n_trials,                 # prevalence
    se_prev  = sqrt(inf_prev * (1 - inf_prev) / n_trials),  # binomial SE
    .groups = "drop" )

# quick plot
B<- grav_prev_summary%>%
drop_na() %>%
ggplot(aes(x = Strain, y = inf_prev, colour = Strain)) +
  geom_point(size = 5) +
  geom_errorbar(
    aes(ymin = inf_prev - se_prev, ymax = inf_prev + se_prev),
    width = 0.2) +
    scale_colour_manual(values = c("#2F6F6B", "#9FD6CC"))+
  ylim(0,1) +
  labs(y = "Infection prevalence, lab assay", x = "")

C<- B/A

ggsave("PARAITE_prev_inten.png", C, height = 7 , width = 4, unit = "in")

```

